---
title: "Lab 07 - Conveying the right message through visualisation"
author: "Thomas Huang"
date: "2026-02-23"
output: github_document
---

### Load packages and data

```{r load-packages, message=FALSE}
library(tidyverse) 
```

### Exercise 1

```{r Ex1}
df <- read_csv("kansas_grouped_rolling_avg.csv")

# Convert long to wide
df_wide <- df %>%
  mutate(mask_mandate = str_replace_all(mask_mandate, " ", "_")) %>% 
  pivot_wider(
    names_from = mask_mandate,
    values_from = rolling_avg
  )

ggplot(df_wide, aes(x = date))+
  geom_line(aes(y = Mask - 11, color = "Mask")) +
  geom_line(aes(y = No_Mask, color = "No Mask")) +
  scale_y_continuous(
    name = "No Mask", limits = c(4, 14),
    sec.axis = sec_axis(~. + 11, name = "Mask")
  )
```

### Exercise 2

```{r Ex2}
ggplot(df_wide, aes(x = date))+
  geom_line(aes(y = Mask, color = "Mask")) +
  geom_line(aes(y = No_Mask, color = "No Mask")) +
   scale_y_continuous(
    name = "No Mask",
    sec.axis = sec_axis(~ . , name = "Mask")
  )
```

### Exercise 3

Mask mandate predicts fewer daily cases. Counties without mask mandate demonstrated a steady trend of daily cases.

### Exercise 4

Wear a mask protects people from getting Covid.

### Exercise 5

I chose a line chart to visualize the trend. My visualization used the same scale for counties with and without mask mandates, which makes the trend comparable. 

### Exercise 6

My misleading visualization aim to show wearing masks actually predicted more cases. I plan to challenge the audience's common sense. Normally, people would assume the axes are positive or increasing. That is, coordinates higher on the y-axis represents larger values. I am going to flip the y-axis.

### Exercise 7

```{r Ex7}
ggplot(df_wide, aes(x = date))+
  geom_line(aes(y = Mask, color = "Mask")) +
  geom_line(aes(y = No_Mask, color = "No Mask")) +
   scale_y_reverse()

# Now I would tweak the scale anchors to make the no mask condition first intersect and then surpass the mask condition.
ggplot(df_wide, aes(x = date))+
  geom_line(aes(y = Mask - 11, color = "Mask")) +
  geom_line(aes(y = No_Mask, color = "No Mask")) +
  scale_y_reverse(
    name = "No Mask", limits = c(4, 14),
    sec.axis = sec_axis(~. + 11, name = "Mask")
  )
```


